### 2012-02-11 docs/notes.tex
Add Gibbs sampling to notes.
small changes

Borrowing from the intuition of stochastic blockmodels, we propose a hierarchical model of continuous time network data that learns latent clusters of nodes which share similar patterns of interaction.  [TODO: Explain how our experiments show that this helps.]  By combining a latent variable framework with a local dependence model for event sequences, we provide a hierarchical approach for modeling event-based network data, accompanying recent hierarchical extensions for latent position models \cite{Handcock2007} and exponential random graph models \cite{Schweinberger2011}.

@@

>>>>

Borrowing from the intuition of stochastic blockmodels, we propose a hierarchical model of continuous time network data that learns latent clusters of nodes which share similar patterns of interaction.  [TODO: Explain how our experiments show that this helps.]   [TODO: perhaps use ``role'' terminology.] By combining a latent variable framework with a local dependence model for event sequences, we provide a hierarchical approach for modeling event-based network data, accompanying recent hierarchical extensions for latent position models \cite{Handcock2007} and exponential random graph models \cite{Schweinberger2011}.

@@

\section{Gibbs sampling}

Let $\mathcal{U}_a = \{a: a \in (i_m,j_m), m \in [1,M]\}$ be the set of events where actor is involved:

$$p(A|z,\beta,a \ \mbox{involved}) = \prod_{a \in \mathcal{U}_a} \lambda_{i_a,j_a}(t_a|\cdot)
\prod_{(i,j) \in \mathcal{R}_{i_a,j_a}} \exp \{ -(t_a - \tau_{ija}) \lambda_{ij}(t_a|cdot)\}$$
